The Wolf in Sheep's Clothing\\ Subversive Adversarial Agent Identification

### 2016-08-04 article.tex
expanded intro

\documentclass[conference]{IEEEtran}
\usepackage[pdftex]{graphicx}
\graphicspath{{images/}}
\usepackage[backend=biber, style=ieee]{biblatex}
%\addbibresource{jprefwolf.bib}
%\addbibresource{mwrefwolf.bib}
\usepackage{amsmath}
\usepackage[final]{microtype}
\usepackage{caption}
\usepackage{glossaries}
\input{glossary.tex}
%\usepackage{hyperref}

@@

Although a system can be tampered with internally

Chain of trusts has been established in the previous works to combat the issue of impersonation, many providing approaches to protecting against malicious alterations to the system. This paper provides three elements of a chain of trust expands on the trust acquired by a robot's individual assessment of new and existing agents by means of communication, state detection and distributed state estimation. The root of trust however relies in a HSE unit which fingerprints specific physical properties and uniquely identifies an agent.

@@

\subsection{Secure State Estimation}
There are three core goals for the security of any cyber-physical system: integrity, availability, and confidentiality \cite{Cardenas2008}. Those can be thought of as three simple questions: "Can I trust the data?", "Do I have access to the data when I need it?", and "Is the data hidden from those who shouldn't have it?". Secure state estimation requires a focus on all three of these pieces.

@@

In order to obtain behavior that is expected and not expected different types of planning have been introduced in literature. Complex environments can be made up of many possible paths which can be computed with strategies such as that of \cite{tallavajhulalist}, where each iteration of path planning uses a more complex predictor. Each of these predictors' path can be used to build a map of states and corresponding behavior that an agent is able to perform. 
Other planning algorithms use specialized planning based on a sub process task such as \cite{bridge2008robust}'s vertical control system, where one module is independently responsible to avoiding objects while more abstract modules can plan according to behavior of objects. Such planning can also be implemented into a map of acceptable behaviors for each state. Multiple goal resolution is attractive as it may still be used in the evaluation of an observed behavior discussed in III.B .

@@

@@

\begin{table}[h]
\label{table_example}
\begin{center}
\begin{tabular}{|c|c|}
\hline
State & Control\\
\hline
$x,y,\theta,v_f,v_theta$ & $a_f,a_\theta$\\
\hline
\end{tabular}
\end{center}
\end{table}

@@

%\printbibliography

>>>>

\documentclass[conference]{IEEEtran}
\usepackage[pdftex]{graphicx}
\graphicspath{{images/}}
\usepackage[backend=biber, style=ieee]{biblatex}
\addbibresource{jprefwolf.bib}
\addbibresource{mwrefwolf.bib}
\usepackage{amsmath}
\usepackage[final]{microtype}
\usepackage{caption}
\usepackage{glossaries}
\input{glossary.tex}
%\usepackage{hyperref}

@@

There are three core goals for the security of any cyber-physical system: integrity, availability, and confidentiality \cite{Cardenas2008}. Those can be thought of as three simple questions: "Can I trust the data?", "Do I have access to the data when I need it?", and "Is the data hidden from those who shouldn't have it?". A system can be tampered through internal and external means. Physical and software components can both be compromised for any given agent internally whereas agents' communications and sensor data are both vulnerable to manipulation externally. We examine the case of external means by first developing a secure channel of communication, then utilizing State estimation and Secure state estimation to obtain a robot's individual assessment of the likelyhood of a robot in questing being compromised. We thus define our threat model further in the first part of the methodology after detailing related works for each of the three components developed. These three components are part of a larger chain of trust that verifies that the internal part of an agent is not compromised by a HSE unit which fingerprints specific physical properties and uniquely identifies an agent.

@@

\subsection{Secure State Estimation}
Secure State Estimation requires a focus on all three of these pieces.

@@

In order to obtain behavior that is expected and not expected different types of planning have been introduced in literature. Complex environments can be made up of many possible paths which can be computed with strategies such as that of \cite{tallavajhula2016list}, where each iteration of path planning uses a more complex predictor. Each of these predictors' path can be used to build a map of states and corresponding behavior that an agent is able to perform. 
Other planning algorithms use specialized planning based on a sub process task such as \cite{ahn2008robust}'s vertical control system, where one module is independently responsible to avoiding objects while more abstract modules can plan according to behavior of objects. Such planning can also be implemented into a map of acceptable behaviors for each state. Multiple goal resolution is attractive as it may still be used in the evaluation of an observed behavior discussed in III.B .

@@

\subsection{Threat Model}

[INSERT THREAT MODEL]

@@

\begin{table}[h]
\label{table_example}
\begin{center}
\begin{tabular}{|c|c|}
\hline
State & Control\\
\hline
$x,y,\theta,v_f,v_\theta$ & $a_f,a_\theta$\\
\hline
\end{tabular}
\end{center}
\end{table}

@@

\printbibliography
